% --- LaTeX CV Template - S. Venkatraman ---

% Set document class and font size
\documentclass[letterpaper, 11pt]{article}
%\documentclass[letterpaper, 11pt]{ujarticle}
\usepackage[whole]{bxcjkjatype}

\usepackage[utf8]{inputenc}
% ニュー・スタンダード!
%\usepackage{xeCJK}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{bm}
%\usepackage{otf}% otf 万能!

% Package imports
\usepackage{setspace, longtable, graphicx, hyphenat, hyperref, fancyhdr, ifthen, everypage, enumitem, amsmath, setspace}

% --- Page layout settings ---

% Set page margins
\usepackage[left=0.5in, right=0.5in, bottom=0.7in, top=0.7in]{geometry}

% Set line spacing
\renewcommand{\baselinestretch}{1.05}

% --- Page formatting ---

% Set link colors
\usepackage[dvipsnames]{xcolor}
\hypersetup{colorlinks=true, linkcolor=RoyalBlue, urlcolor=RoyalBlue}

% Set font to Libertine, including math support
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage{multirow}

% Counter
\newcounter{papercount}
\newcounter{papertype}
\newcommand{\changepapertype}{\setcounter{papercount}{0}\stepcounter{papertype}}
\newcommand{\paperitem}{%
\stepcounter{papercount}%
{\color{OliveGreen}{[\arabic{papertype}.\thepapercount}]}
}
\stepcounter{papertype}%

% Remove page numbering
\pagenumbering{gobble}
\urlstyle{same}
\def\JIF#1{2-year IF: #1}
\def\CT#1{TC: #1}
\def\bJIF#1{\bf{IF:} $\bm{#1}$}
\def\bCT#1{\bf{TC:} $\bm{#1}$}
% --- Document starts here ---

\begin{document}

% Name and date of last update to this document
{
\centering
研究業績目録 (幸若 完壮) \hfill 更新日 10月14日
}
% --- Contact information and other items ---
% Line 1: Email, GitHub, office location
%\noindent \textbf{所属}: Luddy School of Informatics, Computing, and Engineering, Indiana University Bloomington, USA \\
%\textbf{住所}: Myles Brand Hall 919 E 10th St. Bloomington, IN 47408 \\
%\textbf{Eメール}: skojaku@iu.edu  \\
%\textbf{GitHub}: \url{https://github.com/skojaku/}  \\
%\textbf{ホームページ}: \url{https://skojaku.github.io/} \\

% --- Start the two-column table storing the main content ---
% Set spacing between columns
\setlength{\tabcolsep}{3pt}
% Set the width of each column
\setlength\LTleft{0cm}

\subsection*{1.~査読付き学術論文（学術雑誌等に掲載されたもの）}
\begin{longtable}{p{0in}p{2em}p{7in}}
                                                    & \paperitem & \underline{Sadamori Kojaku}, Giacomo Livan, and Naoki Masuda.\\
                                                    & & Detecting anomalous citation groups in journal networks. \\
                                                    & & \textit{Scientific Reports}, 11, 14524, 2021 (\bf{IF}\footnote{2-year window Journal Impact Factor. Web of Science Journal Citation Index 2019 調べ。}$\bm{:~3.998}$, {\bf TC}\footnote{引用数。2021/05/10 Google Scholar調べ。}:0).\\
                                                    & \\

                                                    &\paperitem & \underline{Sadamori Kojaku}, Laurent H\'ebert-Dufresne, Enys Mones, Sune Lehmann, and Yong-Yeol Ahn. \\
                                                    & & The effectiveness of backward contact tracing in networks. \\
                                                    & & \textit{Nature Physics}, 1745-2481, 2021 (\bJIF{19.256}, \bCT{35}).\\
                                                    &
                                                                                                                                                                                                                                                                              \\
                                                    &\paperitem & \underline{Sadamori Kojaku} and Naoki Masuda. \\
                                                    & &  Constructing networks by filtering correlation matrices: a null model approach. \\
                                                    & & \textit{Proceedings of the Royal Society A}, 475, 2231, 2019 (\JIF{2.741}, \CT{3}).\\
                                                    &
                                                                                                                                                                                                                                                                              \\
                                                    &\paperitem & \underline{Sadamori Kojaku}, Mengqiao Xu, Haoxiang Xia, and Naoki Masuda. \\
                                                    & &Multiscale core-periphery structure in a global liner shipping network. \\
                                                    & &\textit{Scientific Reports}, 9, 404, 2019  (\bJIF{3.998}, \bCT{15}).\\
                                                    &
                                                                                                                                                                                                                                                                              \\
                                                    &\paperitem &\underline{Sadamori Kojaku}, Giulio Cimini, Guido Caldarelli, and Naoki Masuda. \\
                                                    & &Structural changes in the interbank market across the financial crisis from multiple core-periphery analysis. \\
                                                    & &\textit{Journal of Network Theory in Finance}, 4, 33-51, 2018 (\bCT{11}).\\
                                                    &
                                                                                                                                                                                                                                                                              \\
                                                    &\paperitem & Naoki Masuda, \underline{Sadamori Kojaku}, and Yukie Sano. \\
                                                    & & Configuration model for correlation matrices preserving the node strength.\\
                                                    & & \textit{Physical Review E}, 98, 012312, 2018 (\JIF{2.296}, \bCT{17}).\\
                                                    &
                                                                                                                                                                                                                                                                              \\
                                                    &\paperitem & \underline{Sadamori Kojaku} and Naoki Masuda. \\
                                                    & &  A generalised significance test for individual communities in networks. \\
                                                    & & \textit{Scientific Reports}, 8, 7351, 2018 (\bJIF{3.998}, \bCT{15}).\\
                                                    &
                                                                                                                                                                                                                                                                              \\
                                                    &\paperitem & \underline{Sadamori Kojaku} and Naoki Masuda. \\
                                                    & & Core-periphery structure requires something else in the network. \\
                                                    & & \textit{New Journal of Physics}, 20, 043012, 2018 (\bJIF{3.539}, \bCT{37}).\\
                                                    &
                                                                                                                                                                                                                                                                              \\
                                                    &\paperitem & \underline{Sadamori Kojaku} and Naoki Masuda. \\
                                                    & & Finding multiple core-periphery pairs in networks. \\
                                                    & & \textit{Physical Review E}, 96, 052313, 2017 (\JIF{2.296}, \bCT{38}).\\
                                                    &
                                                                                                                                                                                                                                                                              \\
                                                    &\paperitem & \underline{Sadamori Kojaku}, Ichigaku Takigawa, Mineichi Kudo, and Hideyuki Imai. \\
                                                    & & Dense core model for cohesive subgraph discovery.\\
                                                    & & \textit{Social Networks}, 44, 143-152, 2016 (\JIF{2.376}, \bCT{11}).\\
                                                    & \\

                                                    &\paperitem & \underline{幸若完壮}, 渡辺 浩太, 五十嵐 一 \\
                                                    & & 合理的な忘却型Profit Sharing強化学習法. \\
                                                    & & 電気学会論文誌Ｃ (電子・情報・システム部門誌), 3, 448-454, 2012 (\CT{0}).\\
\end{longtable}
\subsection*{2.~査読付き国際会議発表論文}
    % --- Section: Publications ---
\changepapertype
\begin{longtable}{p{0in}p{2em}p{5.5in}}
    &\paperitem & \underline{Sadamori Kojaku}, Jisung Yoon, Isabel Constantino, and Yong-Yeol Ahn.
    Residual2Vec: Debiasing graph embedding with random graphs. NeurIPS, 2021 (acceptance rate 26\%). \\
    & & \\
    &\paperitem & *\footnote{* 発表者}Xia Cui, \underline{Sadamori Kojaku}, Naoki Masuda, and Danushka Bollegala. Solving feature spareness in text classification using core-periphery decomposition. In Proceedings of the 7th Joint Conference on Lexical and Computational Semantics, 225-264. New Orleans, USA, 2018 (\CT{3}).\\
    & & \\
    &\paperitem & *Keigo Kimura, Mineichi Kudo, Lu Sun, and \underline{Sadamori Kojaku}. Fast random k-labelsets for large-scale multi-label classification. 23rd International Conference on Pattern Recognition. Cancun, Mexico, December 4-8, 2016 (\CT{0}).\\
    & & \\
    &\paperitem & *\underline{Sadamori Koujaku}, Mineichi Kudo, Ichigaku Takigawa, and Hideyuki Imai.
    Community change detection in dynamic networks in noisy environment.
    24th International Conference on World Wide Web. Florence, Italy, May 18-22, 2015 (\CT{6}).\\
    & \\
    &\paperitem &  *\underline{Sadamori Koujaku}, Mineichi Kudo, Ichigaku Takigawa, and Hideyuki Imai.
    Structual change point detection for social networks.
    The World Congress on Engineering. London, the United Kingdom, July 3-5, 2013 (\CT{7}) {\bf [Best student Award]}.\\
    & \\
    &\paperitem & *\underline{Sadamori Koujaku}, Kota Watanabe, and Hajime Igarashi.
    Adaptive profit sharing reinforcement learning for dynamic environment.
    10th International Conference on Machine Learning and Applications and Workshops. Hawaii, the United States, 2011 (\CT{0}). \\
\end{longtable}

\subsection*{3.~解説・総説}

\changepapertype
\begin{longtable}{p{0in}p{2em}p{5.5in}}
        &\paperitem & \underline{幸若完壮}\\
        & & 埋め込み法が拓くネットワーク科学の新展開. \\
        & & 特集号「複雑ネットワーク研究の最前線」 システム制御情報学会論文誌, 65, 5, 185-191 (2021). \\
\end{longtable}

\subsection*{4.~著書}
なし。

\subsection*{5.~招待講演}

\changepapertype
\begin{longtable}{p{0in}p{2em}p{5.5in}}
    % --- Section: Publications ---
    \changepapertype
    &\paperitem &  *\underline{Sadamori Kojaku}, Livan Giacomo, and Naoki Masuda.
    Detecting anomalous citation groups in journal networks. Science of Innovation and Success Workshop. 2--3 Aug., Waseda University, Japan, 2021.\\
    & & \\
%    &\paperitem & *\underline{Sadamori Kojaku}, Laurent H\'ebert-Dufresne, Enys Mones, Sune Lehmann, and Yong-Yeol Ahn.
%    The effectiveness of backward contact tracing in networks.
%    The State University of New York at Buffalo, 06.04 (2021).\\
%    & & \\
    &\paperitem & *\underline{幸若完壮} ネットワークコアの検出アルゴリズムとその応用. ネットワーク科学セミナー. 統計数理研究所. 8.28-30 (2019). \\
\end{longtable}

\subsection*{6.~その他の論文}

\subsubsection*{査読中}
\changepapertype
\begin{longtable}{p{0in}p{2em}p{5.5in}}
    &\paperitem &  Dakota Murray, Jisung Yoon, \underline{Sadamori Kojaku}, Rodrigo Costas, Woo-Sung Jung, Sta\v{s}a Milojevi\'{c}, and Yong-Yeol Ahn.
    Unsupervised embedding of trajectories captures the latent structure of mobility. \textit{Preprint arXiv}, 2012.02785, 2020. \\
    & & (Science Advancesで審査中)\\
\end{longtable}

\subsubsection*{口頭発表およびポスター発表}
(以下、Proceedingsへの掲載はないが、1,2ページの要旨の審査あり。)
\begin{longtable}{p{0in}p{2em}p{5.5in}}
    &\paperitem & (口頭発表) *\underline{Sadamori Kojaku}, Clara Boothby, Filipi Nascimento Silva, Attila Varga, Xiaoran Yan, Sta\v{s}a Milojevi\'{c}, Alessandro Flammini, Filippo Menczer, and Yong-Yeol Ahn.
    Maping Scientific Foraging. ICSSI. Washinton D.C., USA, 6-9 June (2022).\\
    & & \\
    &\paperitem & (口頭発表) *\underline{Sadamori Kojaku}, Xiaoran Yan, Jisung Yoon, Filipi N. Silva, Vincent Lariviere, and Yong-Yeol Ahn.
    DisamBERT: author name disambiguation with BERT. ICSSI. Washinton D.C., USA, 6-9 June (2022).\\
    & & \\
    &\paperitem &  (口頭発表) *\underline{Sadamori Kojaku}, Xiaoran Yan, Jisung Yoon, Filipi N. Silva, and Yong-Yeol Ahn.
    Disambiguating author names using BERT. Workshop on Natural Language Processing for Scientific Text. 8 Oct., Virtual, 2021 (CT: 0).\\
    & & \\
    &\paperitem &  (口頭発表) *\underline{Sadamori Kojaku}, Jisung Yoon, and Yong-Yeol Ahn.
    residual2vec: a bias-corrected embedding for graphs. International Conference on Computational Social Science. 27-31 July, ETH Zurich, 2021 (CT: 0).\\
    & & \\
%    &\paperitem &  (査読中) Dakota Murray, Jisung Yoon, \underline{Sadamori Kojaku}, Rodrigo Costas, Woo-Sung Jung, Sta\v{s}a Milojevi\'{c}, and Yong-Yeol Ahn.
%    Unsupervised embedding of trajectories captures the latent structure of mobility. \textit{Preprint arXiv}, 2012.02785, 2020 \\
%    & \\
    &\paperitem & (口頭発表) \underline{Sadamori Kojaku}, Laurent H\'ebert-Dufresne, Enys Mones, Sune Lehmann, and *Yong-Yeol Ahn.
    The effectiveness of backward contact tracing in networks. NetSci. Virtual, 05-10 July (2021).\\
    & & \\
    &\paperitem &  (口頭発表) *\underline{Sadamori Kojaku}, Jisung Yoon, and Yong-Yeol Ahn.
    Residual2Vec: A null model approach for graph embedding. NetSci. Virtual, 05-10 July (2021).\\
    & & \\
    &\paperitem & (ポスター) *Isabel Constantino, \underline{Sadamori Kojaku}, Santo Fortunato, and Yong-Yeol Ahn.
    Embedding the disciplinary structure of physics. NetSci. Virtual, 05-10 July (2021).\\
    & & \\
    &\paperitem &  (口頭発表) Dakota Murray, *Jisung Yoon, \underline{Sadamori Kojaku}, Rodrigo Costas, Woo-Sung Jung, Sta\v{s}a Milojevi\'{c}, and Yong-Yeol Ahn.
    Unsupervised embedding of trajectories captures the latent structure of mobility.  NetSci. Virtual, 05-10 July (2021).\\
    & & \\
    &\paperitem & (口頭発表) *\underline{Sadamori Kojaku}, Attila Varga, Xiaoran Yan, Filipi N. Silva, Staša Milojević, Alessandro Flammini, and Yong-Yeol Ahn. The landscape of the COVID-19 research: A neural embedding approach. Netsci. Rome, Italy, 17-25 September (2020).\\
    & & \\
    &\paperitem & (口頭発表) *\underline{Sadamori Kojaku}, Giacomo Livan, and Naoki Masuda. Detecting citation cartels in journal networks. Netsci. Rome, Italy, 17-25 September (2020).\\
    & & \\
    &\paperitem & (口頭発表) *Shaunette Ferguson, \underline{Sadamori Kojaku}, and Teruyoshi Kobayashi. Diurnal dynamics of financial systemic risk. Netsci-X. Tokyo, Japan, 20-23 January (2020).\\
    & & \\
    &\paperitem & (口頭発表) *\underline{Sadamori Kojaku}, Giulio Cimini, Guido Caldarelli, and Naoki Masuda. Structural changes in the interbank market across the financial crisis from multiple core-periphery analysis. Netsci. Vermont, U.S., May 26-31 (2019).\\
    & & \\
    &\paperitem &  (ポスター発表) *\underline{Sadamori Kojaku} and Naoki Masuda. Constructing networks from correlation matrices: An application to economical data. Threshold Networks. Nottingham 22-24 July (2019).\\
    & & \\
    &\paperitem & (口頭発表) *\underline{Sadamori Kojaku} and Naoki Masuda. Core-periphery structure in degree-heterogeneous networks. Netsci-X. Hangzhou, China (2018).\\
    & & \\
    &\paperitem &  (ポスター発表) *\underline{Sadamori Kojaku} and Naoki Masuda. A generalised significance test for individual communities in networks. Netsci. Paris, France, June 11-15 (2018).\\
    & & \\
    &\paperitem & (ポスター発表) *\underline{Sadamori Kojaku} and Naoki Masuda. Multi-scale organisation of core-periphery structure in networks. 1st Latin American Conference on Complex Networks. Puebla, Mexico September 25-29 (2017).\\
    & & \\
    &\paperitem & (ポスター発表) *\underline{Sadamori Kojaku} and Naoki Masuda. Core-periphery structure of networks: Consideration for random heterogeneous networks. Netsci. Indianapolis, Indiana, USA (2017).\\
    & & \\
    &\paperitem & (ポスター発表) *\underline{Sadamori Kojaku} and Naoki Masuda. An extension of modularity for finding multiple core/periphery structure in networks. Netsci-X. Tel Aviv, Israel January 15-18 (2017) {\bf [Best Contribution on Finantial Networks Award]}.\\
    & & \\
    &\paperitem & (口頭発表) *\underline{Sadamori Kojaku} and Naoki Masuda. Finding multiple core-periphery structure with random walks. 5th International Workshop on Complex Networks and their Applications. Milan, Italy November 30-December 2 (2016).\\
\end{longtable}

\subsection*{7.~特許等}
\changepapertype
\begin{longtable}{p{0in}p{2em}p{5.5in}}
    & \paperitem & \underline{幸若完壮}, 上東貴志. 学術論文の査読者検索装置、査読者検索方法、及び査読者検索プログラム. 特願2020-14904, 2020\\
    & &\\
    & \paperitem & Prediction method, prediction system and program. Patent No: 9087294, 2011\\
    & & \\
\end{longtable}


\subsection*{8.~受賞等}
\changepapertype

\begin{longtable}{p{0in}p{2em}p{5.5in}}
    &\paperitem & Best Contribution on Financial Networks Award. \textit{NetSci-X} {[発表者58人中1人]}. \hfill 2017\\
    & & \\
    &\paperitem & 研究科科長賞. \textit{北海道大学大学院情報科学研究科}\hfill 2015 \\
    & & \\
    &\paperitem & Best Student Award. \textit{The World Congress on Engineering} \hfill 2013\\
    & & \\
\end{longtable}

\subsection*{9.~競争的獲得資金の獲得状況}
\changepapertype
\begin{longtable}{p{0in}p{2em}p{5.5in}}
    &\paperitem & \underline{Sadamori Kojaku}, Giulio Cimini, Guido Caldarelli, Daigo Uemoto, and Takashi Kamihigashi. Correlation-based reconstruction of financial networks for systemic risk control. 代表者: 幸若 完壮, Giulio Cimini. JSPS二国間(日本-イタリア)交流事業。 (海外転出のため辞退) \hfill 2020.\\
    & & \\
\end{longtable}

\subsection*{10.~その他研究業績}
\changepapertype
\begin{longtable}{p{0in}p{2em}p{5.5in}}
    &\paperitem & \textbf{(査読)} Nature communications; Scientific Reports; Journal of Complex Networks; Journal of Computational Social Science; PLOS ONE.\\
    && \\
    &\paperitem & \textbf{(国際会議プログラム委員)} International Conference on Network Science, 2020\\ &&\url{https://netsci2020.netscisociety.net/organizers/}\\
    && \\
    &\paperitem & \textbf{(国際会議運営)} International Conference on Network Science X, 2020 (Web担当)\\ && \url{https://netscix2020tokyo.github.io/index.php/organizers/}\\
    & & \\
\end{longtable}
%
%\subsection*{その他の研究業績}
%
%\changepapertype
%\begin{longtable}{p{0in}p{2em}p{5.5in}}
%    \multirow{2}{1in}{{\color{OliveGreen}{SERVICE}}}
%                                                    &\paperitem & \textbf{Referee work}: Nature communications; Scientific Reports; Journal of Complex Networks; Journal of Computational Social Science; PLOS ONE \\
%                                                    &\paperitem & \textbf{Program committee}: International Conference on Network Science, 2020 \\
%                                                    &\paperitem & \textbf{Organizing committee}: International Conference on Network Science X, 2020 \\
%                                                    & & \\
%\end{longtable}
    % --- End of CV! ---
\end{document}
